Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-11 Mag_quotients.tex
MAJ

We define the \Def{anti-associative operad} by
\begin{equation}
  \label{equ:anti-associative_operad}
  \AAs:=\KMag/_{\IAAs}
\end{equation}
where $\IAAs$ is the ideal spanned by
\begin{math}
  \LComb{3}+\RComb{3}
\end{math}.
\Todo{Illustrer avec la représentation graphique ?}
\medbreak

\begin{Lemma}
\label{lem:properties_of_AAs}
\end{Lemma}

\begin{proof}
\Todo{todo}
\end{proof}
\medbreak

@@

Finally, for every integer $\gamma\geq 2$, we define the
\Def{$\gamma$-right comb operad} $\RC{\gamma}$ as follows. For every
arity $n$, we let
\begin{equation}
  \label{equ:compositions_of_RC}
  \RC{\gamma}(n):=
    \begin{cases}
        \KMag(n) &
        \mbox{if } n \leq \gamma, \\
        \K\Angle{\RComb{n}}
            & \mbox{otherwise},
    \end{cases}
\end{equation}
and the partial composition $\Tfr_1 \circ_i \Tfr_2$ is the partial
composition of $\Tfr_1$ and $\Tfr_2$ in $\Mag$ if the integer
\begin{math}
  n:=|\Tfr_1|+|\Tfr_2| 
\end{math}
is smaller than or equal to $\gamma$, and $\RComb{n}$, otherwise.
\medbreak

>>>>

We define the \Def{anti-associative operad} by
\begin{equation}
  \label{equ:anti-associative_operad}
  \AAs:=\KMag/_{\IAAs}
\end{equation}
where $\IAAs$ is the ideal spanned by
\begin{math}
  \LComb{2}+\RComb{2}
\end{math}.
\Todo{Illustrer avec la représentation graphique ?}
Using the Buchberger algorithm for operads~\cite[Section 3.7]{DK10}, we
check that the set of rewrite rules
\begin{equation}
  \label{equ:convergent_presentation_of_AAS}
  \left\{\LComb{2}\Rew -\RComb{2},\
  \RComb{3}\Rew 0
  \right\}
\end{equation}
is a convergent presentation of $\AAs$. We point out that this statement
is false if the characteristic of $\K$ is equal to $2$. Moreover, using
the convergent presentation~\eqref{equ:convergent_presentation_of_AAS},
we have
  \begin{equation}
    \label{equ:Hilbert_series_of_AAS}
    \HilbertSeries_{\AAs}(t)=t+t^2+t³.
    \end{equation}
\medbreak

@@

Finally, for every integer $\gamma\geq 2$, we define the
\Def{$\gamma$-right comb operad} $\RC{\gamma}$ as follows. For every
arity $n$, we let
\begin{equation}
  \label{equ:compositions_of_RC}
  \RC{\gamma}(n):=
    \begin{cases}
        \KMag(n) &
        \mbox{if } n \leq \gamma, \\
        \K\Angle{\RComb{n}}
            & \mbox{otherwise},
    \end{cases}
\end{equation}
and the partial composition $\Tfr_1 \circ_i \Tfr_2$ is the partial
composition of $\Tfr_1$ and $\Tfr_2$ in $\Mag$ if the integer
\begin{math}
  n:=|\Tfr_1|+|\Tfr_2| 
\end{math}
is smaller than or equal to $\gamma$, and $\RComb{n}$, otherwise.
Moreover, by definition of the $\gamma$-right comb operad, we have
\begin{equation}
  \label{equ:Hilbert_series_of_RC}
  \HilbertSeries_{\RC{\gamma}}(t)=\sum_{1\leq n\leq\gamma}\Catalan(n) t^n
  +\sum_{n\geq\gamma+1}t^n.
  \end{equation}
\medbreak
